\mytitle

### 2023-05-05 chapters/jitsynth/rebuttal.txt

We thank the reviewers for their insightful feedback. We will use it to revise
the paper. Below, we answer the questions from each of the reviews.

---R1---

> Future research in speeding up synthesis could very likely complement the
  approaches presented here. ... Perhaps combining these techniques with
  peephole superoptimizers would help.

Yes, we also believe that these are promising directions for future work, and
that they can help improve the performance of both the synthesis process and the
synthesized JITs.

> It would be great if [the code] were [publicly] available.

We plan to submit an artifact if the paper is accepted. We will
also make the code and all of our benchmarks publicly available.

---R2---

> Why [87 out of 102 eBPF instructions] enough for the compiler to
  be useful? ... How many real eBPF programs require just those 87 instructions
  (how many of your test programs used an instruction you didn't handle?)

These 87 instructions cover 228/244 (~93%) of the eBPF programs in the
test suite in the Linux kernel (lib/test_bpf.c). They are also sufficient
to run all the application benchmarks from the Jitk project (Fig. 7). We
will clarify this in the revision.

> Page 12 [says] that the sketch for addi32 includes 2^350 programs,
  but ... that number seems far too low.

Yes, 2^350 is much lower than the number of all programs at this tree depth and
program length. We got this lower number by including some simple optimizations
in the naive sketch, such as reusing symbolic constants.

> Bugs in Definitions 8 and 9.

Yes, these are indeed bugs in the definitions; thanks for catching them!  The
implementation matches the intuition provided in the text, and we will fix the
definitions accordingly.

> Is strong soundness equivalent to soundness?  Are there any compilers that are
  sound but not strongly sound? It looks ... like every sound compiler is
  strongly sound.

This is a great question. While the logical formulas for soundness and strong
soundness aren't equivalent, we could not think of any case in which a compiler
is sound but not strongly sound. For that reason, we also strongly suspect that
using strong soundness won't miss (m)any real compilers.

> A 2.28x slowdown is fairly significant, so it's a bit strong to say
that "the performance is similar to the existing Linux compiler".

Agreed, we will tone down this claim. This kind of slowdown would be okay
for some eBPF programs (e.g., for system-call filtering), but not for
high-performance network filtering. For the latter, it would be necessary
to get the performance on par with that of the hand-written compiler.

> [Did you try] to synthesise compilers that don't use bitvector constants
  ... or that use small constants ... as one of your intermediate sketches?

> [Did you try] to generate mini-compilers for common sequences of
  instructions, or ... a peephole optimiser for some common constructs?

These are great suggestions. While we haven't tried them, we believe that they
would improve synthesis performance as well as the performance of the generated
code.

---R3---

Thanks for the review! We agree that more work is needed before automatically
generated JITs can replace the ones written by hand.

---R4---

> How easy is it to extend the compiler to handle dynamic register allocation?

This would be quite difficult, as it breaks our core assumption that a static
register mapping exists from the source to target language, which is a common
practice for in-kernel JITs.

> You mentioned a way to use pre-defined micros/subroutines as a way to simplify
  compilation of commonly used and/or complex instructions. Should these
  micros/subroutines be verified for correctness and security?

These pre-defined macros are also synthesized by JitSynth, and they are verified as
part of the synthesis process. We will clarify this in any future revisions.

>  It would be interesting to compare and combine this work with Ironclad Apps
   ... and [allow] the compiler developer to interact with the synthesis tool and
   guide the generation.

We agree that these are interesting directions for future work; thanks for the
suggestions!

### 2023-05-05 thesis.tex
All depsynth compile issues fixed
acks, jitsynth, dmacros

%% Added by Jacob
\usepackage{makecell}
%%%%%%%%%%%%%%%%

@@

\usepackage{amsmath}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{proof}{Proof}[chapter]

@@

This thesis covers work done in the final year and a half of my PhD.
The work done before then,
 largely with the Molecular Information Systems Lab at UW,
 was and is a great source of pride.
I am very fortunate to enjoy the
 endlessly supportive mentorship of my advisor Luis Ceze,
 who is the very first person you want on your team,
 and who introduced me to
 the collaborative, cross-disciplinary environment at MISL.

On the \egg side of things,
 I owe the all the fun and any success
 I had to the entire PLSE group.
Thanks especially to Zach Tatlock,
 without whom PLSE would simply not be the same.
The main component of this thesis is the \egg
 paper, and my co-authors
 in that work deserve a special shoutout for making
 that project what it is:
 Chandrakana Nandi,
 Remy Wang,
 Oliver Flatt,
 Zach Tatlock,
 and Pavel Panchekha.

Thanks to my friends and family for
 making this journey possible and even enjoyable.
And finally,
 thank you Sami for doing this whole thing with me.

@@

\pagestyle{headings}
\setcounter{page}{1}
\pagenumbering{arabic}
\renewcommand{\chaptermark}[1]{\markboth{\sc{\chaptername\ \thechapter.\ #1}}{}}
\renewcommand{\sectionmark}[1]{\markright{\sc{\thesection.\ #1}}{}}
% \listoftodos
%\input{chapters/01-intro}
%\input{chapters/02-background}
%\input{chapters/03-rebuilding}
%\input{chapters/04-analyses}
%\input{chapters/05-egg}
%\input{chapters/06-case-studies}
%\input{chapters/99-conclusion}
\input{chapters/depsynth/depsynth}

>>>>

%% Added by Jacob
\usepackage{makecell}
%\usepackage{amsthm}
%\theoremstyle{acmdefinition}
%\@ifundefined{example}{%
%}{}
%%%%%%%%%%%%%%%%

@@

\usepackage{amsmath}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{example}{Example}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{proof}{Proof}[chapter]

@@

% Emina
Over the past five years, I've had the priviledge of working with
of Emina Torlak. She is everything I could have possibly asked for
in a mentor. From getting into the Rosette weeds to career chats over Molly Moon's,
she always seems to know exactly what I need to hear and when I need to hear it.
Thanks for always believing me and keeping me moving forward.

% James
Before I ever started my PhD at UW, I saw James Bornholt give a talk at PLDI 2017
about his work synthesizing memory models. Of course I loved the talk,
but at the time, I had no idea how much of an impact James' work would
have on my life. Without the groundwork of James' ridiculously prolific
career, this thesis would not exist. As if this wasn't enough, James has
also been an excellent mentor and friend throughout my time at UW. 
Thanks for working with me, James.

% Isil
My path to writing this thesis feels like a series of insanely lucky
happenstances. Starting my undergraduate degree at UT Austin
the same semester that Isil Dillig became a faculty member at UT wasn't the
first or last bit of this luck, but it certainly was one of the most impactful.
Isil is the reason that I started my program synthesis research journey, and I
likely never would have pursued a PhD without her guidance.
% TODO conclude?

% Collabs
I'm extremely grateful to everyone that I've worked with during my time at UW.
Without fail, Xi Wang always asks the most important and challenging questions,
and I wouldn't be half the researcher I am today without him.
Luke Nelson brought me up to speed when I started in the UNSAT group at UW,
and for that I'll always be thankful.
Additionally, I'd like to thank Zach Tatlock and Shane Steinert-Threlkeld
for agreeing to be part of my thesis committee.
Zach, thanks for making me feel at home in new, scary surroundings.

% Unsat + PLSE
I doubt I could have finished this PhD with my sanity intact without the support
of all my friends from the UNSAT group, PLSE lab, Systems lab, and Architecture
group. There are so many amazing people that have welcomed me into these communities,
but especially to
Oliver Flatt,
Ben Kushigian,
Katie Lim,
Ellis Michael,
Samantha Miller,
Chandrakana Nandi,
Pratyush Patel,
Dan Petrisko,
Sorawee Porncharoenwase,
Max Ruttenberg,
Gus Smith,
Ewin Tang,
and Max Willsey,
thank you for making these past five years a blast.

% Fam + Madeline
Finally, I cannot emphasize how crucial the love and support from my family
has been over the past five years. My parents Shiela and Steve and my brothers
Daniel and Sammy have been a non-stop source of encouragement.
Madeline, I'll never be able to thank you enough for sticking through this whole
journey with me, but I will certainly try. Thank you for always being on my team.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\pagestyle{headings}
\setcounter{page}{1}
\pagenumbering{arabic}
\renewcommand{\chaptermark}[1]{\markboth{\sc{\chaptername\ \thechapter.\ #1}}{}}
\renewcommand{\sectionmark}[1]{\markright{\sc{\thesection.\ #1}}{}}
% \listoftodos
\input{chapters/intro}
\input{chapters/jitsynth/jitsynth}
\input{chapters/depsynth/depsynth}
